True versus apparent shapes of astrophysical bow shocks

### 2017-03-20 papers/Paper1/sec-quadrics-observations.tex
Initial outline of MIPSGAL section of paper
Just figures so far

>>>>

\subsection{Mid-infrared arcs around early-type stars}
\label{sec:mid-infrared-arcs}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/mipsgal-r0-r0}
  \caption[]{Comparison of the bow sock sizes determined from our fits
    with those given by Kobulnicky for the MIPSGAL sources.}
  \label{fig:mipsgal-sizes}
\end{figure}

\begin{figure*}
  \centering
  \begin{tabular}{ll}
    (a) & (b) \\
    \includegraphics[width=0.45\textwidth]{figs/mipsgal-Rc-R90-zoom} &
    \includegraphics[width=0.45\textwidth]{figs/mipsgal-Rc-R90-thumbnails} 
  \end{tabular}
  \caption[]{MIPSGAL sources on the bow shock shape diagnostic
    diagram.  (a) Individual sources.  (b) Kernel density estimate of
    the distribution.}
  \label{fig:mipsgal-shapes}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{figs/mipsgal-pairplot}
  \caption[]{Correlations between non-shape parameters of MIPSGAL sources.}
  \label{fig:mipsgal-pairplot}
\end{figure*}

\begin{figure*}
  \centering
  \begin{tabular}{ll}
    (a) & (b) \\
    \includegraphics[width=0.45\textwidth]{figs/mipsgal-Rc-R90-R0} &
    \includegraphics[width=0.45\textwidth]{figs/mipsgal-Rc-R90-Mag} 
  \end{tabular}
  \caption[]{Significant correlation of bow shock shape with (a) bow
    shock angular size, and (b) extinction-corrected magnitude of
    stellar source.}
  \label{fig:mipsgal-correlated}
\end{figure*}

\begin{figure*}
  \centering
  \begin{tabular}{ll}
    (a) & (b) \\
    \includegraphics[width=0.45\textwidth]{figs/mipsgal-Rc-R90-environment} &
    \includegraphics[width=0.45\textwidth]{figs/mipsgal-Rc-R90-candidates} 
  \end{tabular}
  \caption[]{Lack of significant correlation of bow shock shape with
    (a) environment, and (b) uncertainty in stellar source
    identification.}
  \label{fig:mipsgal-uncorrelated}
\end{figure*}

\subsection{Far-infrared arcs around late-type stars}
\label{sec:far-infrared-arcs}

\subsection{Stationary emission line arcs in M42}
\label{sec:stat-emiss-line}
